HBCC - DLPFC - FEATURECOUNTS - GRCh38 - CQN - Sparse Model

### 2019-12-28 cmc-rnaseq-de/HBCC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
automate outlier id - 4SDs from mean
update to sep2019 ENSEMBL host

# Define biomart object
mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", host = "oct2018.archive.ensembl.org", dataset = "hsapiens_gene_ensembl")

@@

Based on the expression pattern following samples were tagged as outliers: `r paste(indToRemove, collapse = ', ')`

@@

WGCNA::plotDendroAndColors(tree, 
                           colors = cols, 
                           dendroLabels = FALSE, 
                           abHeight = 0.80, 
                           main = "Sample dendrogram",
                           groupLabels = colnames(COVARIATES.tmp[,c('Dx')]))
```

>>>>

# Define biomart object
mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", host = "sep2019.archive.ensembl.org", dataset = "hsapiens_gene_ensembl")

@@

Based on the expression pattern following samples were tagged as outliers: `r paste(outliers, collapse = ', ')`

@@

WGCNA::plotDendroAndColors(tree, 
                           colors = cols, 
                           dendroLabels = FALSE, 
                           abHeight = 0.80, 
                           main = "Sample dendrogram",
                           groupLabels = "Dx")
```
